Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-10-11 rmd/Manuscript.Rmd
Modified little details in the manuscript

```{r}
# Just to get pipa vessels that fished inside pipa before 2015
pipa_vessels <- effort_by_vessel %>% 
  filter(treated) %$%
  unique(mmsi) %>% 
  length()
```

@@

eez <- read_sf(dsn = here::here("data", "spatial", "EEZ_subset"),
               layer = "EEZ_subset")

@@

```{r, fig.cap = "\\label{fig:redist_trend_ps}Monthly relative allocation of fishing effort by PIPA-fishing vessels before and after PIPA for 9 EEZs, PIPA, the high seas and 'other EEZs'."}
displacement_data %>% 
  filter(gear == "purse_seines") %>% 
  ggplot(aes(x = date, y = h_prop, group = post)) +
  geom_smooth(method = "lm", color = "black", size = 0.5, linetype = "dashed") +
  geom_point(size = 1) +
  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
  scale_fill_brewer(palette = "Paired") +
  ggtheme_plot() +
  facet_wrap(~country, scales = "free_y")
```

@@

```{r, fig.cap = "\\label{fig:redist_trend_spa}Proportion of fishing hours that all vessels spent on each of the EEZs and the high seas.", eval = F}
pipa_map_disp <- pipa %>% 
  mutate(country = "PIPA") %>% 
  left_join(displacement_data, by = "country")

# Los colores del mapa deben estar dados por el Post:Country
eez %>% 
  left_join(displacement_data, by = c("ISO_Ter1" = "country")) %>%
  group_by(year) %>% 
  summarize(h_prop = mean(h_prop, na.rm = T)) %>% 
  ggplot() +
  geom_sf(aes(fill = h_prop, linetype = PNA), size = 1, color = "black") +
  geom_sf(data = pipa_map_ba_disp, aes(fill = h_prop), linetype = "dashed", color = "red") +
  ggtheme_plot() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(10)) +
  facet_wrap(~year)
```

```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
pipa_map_ba_disp <- pipa %>% 
  mutate(country = "PIPA") %>% 
  left_join(ba_disp_ps, by = "country")

# Los colores del mapa deben estar dados por el Post:Country
eez %>% 
  left_join(ba_disp_ps, by = c("ISO_Ter1" = "country")) %>%
  filter(!is.na(change)) %>% 
  ggplot() +
  geom_sf(aes(fill = change), color = "black") +
  geom_sf(data = pipa_map_ba_disp, aes(fill = change), linetype = "dashed", color = "red") +
  ggtheme_plot() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
```

>>>>

```{r}
# Just to get pipa vessels that fished inside pipa before 2015
pipa_vessels <- effort_by_vessel %>% 
  filter(treated, baci_strict) %$%
  unique(mmsi) %>% 
  length()
```

@@

eez <- read_sf(dsn = here::here("data", "spatial", "regions"),
               layer = "regions")

@@

```{r, fig.cap = "\\label{fig:redist_trend_ps}Monthly relative allocation of fishing effort by PIPA-fishing vessels before and after PIPA for 9 EEZs, PIPA, the high seas and 'other EEZs'."}
displacement_data %>% 
  filter(gear == "purse_seines",
         h_prop > 0) %>%
  # mutate(country = as.character(country),
         # country = ifelse(country %in% c("PIPA", "KIR", "HS", "ASM", "COK", "FSM", "MHL", "NRU", "PNG", "SLB", "TKL", "TUV", "UMI"), country, "OTH"),
         # country = forcats::fct_relevel(country, "OTH", after = Inf)) %>% 
  ggplot(aes(x = date, y = h_prop, group = post)) +
  geom_smooth(method = "lm", color = "black", size = 0.5, linetype = "dashed") +
  geom_point(size = 1) +
  geom_vline(xintercept = lubridate::date(paste(2015, 1, 1, sep = "/")), linetype = "dashed") +
  scale_fill_brewer(palette = "Paired") +
  ggtheme_plot() +
  facet_wrap(~country, scales = "free_y")
```

@@

```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}

# Los colores del mapa deben estar dados por el Post:Country
eez %>% 
  left_join(ba_disp_ps, by = c("id" = "country")) %>%
  # filter(!is.na(change)) %>% 
  ggplot() +
  geom_sf(aes(fill = change), color = "black") +
  ggtheme_plot() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(10))
```

### 2018-10-11 slides/ERE_lunch.Rmd
Modified little details in the manuscript

---
title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
author:
  - Juan Carlos Villaseñor-Derbez^1^
  - John Lynham^2^
institute:
  - ^1^Bren School of Environmental Science and Management, UC Santa Barbara
  - ^2^Department of Economics, University of Hawaii at Manoa
date: "5/10/2018"
output: 
  beamer_presentation: 
    slide_level: 2
    citation_package: biblatex
bibliography: references.bib
biblio-style: authoryear
header-includes:
  - \usepackage{booktabs}
---

>>>>

---
title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
author:
  - Juan Carlos Villaseñor-Derbez^1^
  - John Lynham^2^
institute:
  - ^1^Bren School of Environmental Science and Management, UC Santa Barbara
  - ^2^Department of Economics, University of Hawaii at Manoa
date: "5/10/2018"
output: 
  beamer_presentation: 
    citation_package: biblatex
    slide_level: 2
    theme: Berkeley
bibliography: references.bib
biblio-style: authoryear
header-includes:
  - \usepackage{booktabs}
---
